---
title: "Productivity and reproducbility"
author: "Olivia Boven"
date: "2023-09-14"
output:
  pdf_document: default
  word_document: default
subtitle: An example using *palmerpenguins*
latex_engine: xelatex
bibliography: references.bib
csl: apa.csl
geometry: margin=1in
header-includes: "-\\usepackage{setspace} -\\doublespacing -\\usepackage{lineno} -\\linenumbers
  -\\usepackage{float} -\\usepackage{fontspec} -\\setmainfont{Times New Roman}"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(palmerpenguins)
```
\newpage

# Abstract

Who doesn't like penguins? Here we look at bill length and depth to demonstrate reproducible science.

\newpage

# Introduction

This short project focuses on the widely used *palmerpenguins* package [@horstPalmerArchipelagoPenguins2022] with the intention of making an entirely reproducible workflow. The penguins near Palmer Station, Antarctica, such as Adelie penguins (*Pygoscelis adeliae*) have been the focus of many studies [@nardelliKrillAvailabilityAdjacent2021; @ciminoLongtermPatternsEcosystem2023]. Since the development of the *palmerpenguins* package, data on these penguins has been used in many coding examples. As such, it was chosen for this demonstration of reproducible research. We will determine whether bill length and depth vary between species.

# Methods

We plotted bill length against bill depth for each species in RStudio using *plot* to visually assess whether bill length and depth varied between species. 

# Results

Our results indicate that bill length and depth does vary between species (Figure 1).

# Discussion

Bill length and depth varied between species, possibly because they are different species that have evolved independently, faced different selective pressures, and are optimized for non-identical niches. 

# References
:::{#refs}
:::

# Figure captions

Figure 1. Bill depth versus bill length for Adelie, Chinstrap, and Gentoo penguins.

# Figures

```{r, echo=FALSE, echo=FALSE, warnings=FALSE}
colours <- data.frame (species  = c("Adelie", "Chinstrap", "Gentoo"),
                       color = c("darkorange", "blue", "cyan2")
)
penguins_col <- merge(x=penguins, y=colours, by="species", all.x=TRUE)
plot(penguins_col$bill_depth_mm, penguins_col$bill_length_mm, pch=16, col= penguins_col$color, xlab = "Bill depth (mm)", ylab = "Bill length (mm)")
```

Figure 1. 
